Scikit-learn: API design for machine learning

### 2013-06-19 paper.tex
floating figure for k-means example too
XXX there's an asymmetry between the examples now...

The \textit{predictor} interface extends the notion of an estimator
by adding a \texttt{predict}
method that takes an array \texttt{X\_test} and produces
predictions for \texttt{X\_test}, based on the learned parameters of the
estimator (we call the input to \texttt{predict} ``\texttt{X\_test}'' in order
to emphasize that \texttt{predict} generalizes to new data). In the case of
supervised learning estimators, this method typically returns the predicted
labels or values computed by the model.  Continuing with the previous example,
predicted labels for \texttt{X\_test} can be obtained using the following
snippet:
\begin{pythoncode}
y_pred = clf.predict(X_test)
\end{pythoncode}
Some unsupervised learning
estimators may however also implement that interface, as illustrated below:
\begin{pythoncode}
from sklearn.cluster import KMeans

km = KMeans(n_clusters=10)
km.fit(X_train)
clust_pred = km.predict(X_test)
\end{pythoncode}
In the above example, a \texttt{KMeans} estimator is first fit on the training
data \texttt{X\_train}. Then the \texttt{predict} method is called on the test
data \texttt{X\_test} in order to retrieve predicted cluster labels.
The \texttt{predict} method in \sklearn thus offers a unified way
to compute predictions with respect to unseen data.

>>>>

The \textit{predictor} interface extends the notion of an estimator
by adding a \texttt{predict}
method that takes an array \texttt{X\_test} and produces
predictions for \texttt{X\_test}, based on the learned parameters of the
estimator (we call the input to \texttt{predict} ``\texttt{X\_test}'' in order
to emphasize that \texttt{predict} generalizes to new data). In the case of
supervised learning estimators, this method typically returns the predicted
labels or values computed by the model.  Continuing with the previous example,
predicted labels for \texttt{X\_test} can be obtained using the following
snippet:
\begin{pythoncode}
y_pred = clf.predict(X_test)
\end{pythoncode}

Some unsupervised learning
estimators may however also implement the \texttt{predict} interface.
The code in Figure~\ref{kmeans-predict} fits a $k$-means model with $k=10$
on training data \texttt{X\_train},
then uses the model's \texttt{predict} method
to obtain cluster labels for unseen data \texttt{X\_test}.

\begin{figure}[h]
\begin{pythoncode}
from sklearn.cluster import KMeans

km = KMeans(n_clusters=10)
km.fit(X_train)
clust_pred = km.predict(X_test)
\end{pythoncode}
\caption{Finding closest centroids for unseen data after $k$-means clustering.
         \texttt{clust\_pred} will hold integer indices of centroids.}
\label{kmeans-predict}
\end{figure}
